---
title: "How did Heat Wave in 2018 Influence Agricultural Vegetation in Demmin?"
author: "Haiyin Ye"
date: "29 April 2019"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)# set working directory
```

## Introduction
In 2018, Germany experienced the warmest spring and summer seasons since 1881, according to the report of "drought & heat wave summer 2018 (Germany)" (Mühr et al. 2018). As one of the major envionmental disasters, drought is always a big topic in agriculture. This study is focused on temperature as an environmental indicator and the change in the growth of agricultural vegetation during heat wave. 

## 3 sub-questions

- Did the variation pattern of NDVI and LAI change? And how?
- Did the variation pattern of temperature change? And how?
- How are these two changes related?

## Study Area

agricultural fields in Alt Tellin, Demmin, Germany 

```{r studyarea}
renderPlot({

library(raster)
library(rgdal) 
## reloading function
reloading <- function(stack){
  in_stack <- brick(stack)
  band_names <- c("pixel_qa", "radsat_qa", "aerosol_qa", "Aerosol", "Blue", "Green", "Red", "NIR", "SWIR.1", "SWIR.2")
  names(in_stack) <- band_names
  return(in_stack)
}
stack20180520 <- reloading("stack20180520.tif")
ww <- readOGR("WW3.shp")
ww2 <- spTransform(ww,CRS(proj4string(stack20180520)))
ww_felder <- readOGR("WW-felder.shp")
ww_felder <- spTransform(ww_felder,CRS(proj4string(stack20180520)))
plotRGB(stack20180520,  r="Red", g="Green", b="Blue", stretch="lin")
plot(ww_felder, col="yellow", add=TRUE)
plot(ww2, col="red", add=TRUE)
})

```

## Data Source
- Landsat 8 OLI/TIRS C1 Level-2 Products (USGS) => NDVI/LAI
- ERA Interim (ECMWF) => daily temperature


## NDVI & LAI
The change in vegetation growth could be observed by the change in NDVI (Normalized Difference Vegetation Index) and LAI (Leaf Area Index).

## NDVI & LAI
```{r ndvi, echo=TRUE}
## NDVI function ##

NDVI <- function(stack){
  # get NIR & Red bands
  nir <- stack[["NIR"]]
  red <- stack[["Red"]]
  # calculate NDVI
  NDVI <- (nir-red) / (nir+red)
  return(NDVI)
}

## LAI function ##

LAI <- function(ndvi){0.57*exp(2.33*ndvi)}  # Saito et al (2001)

```

## NDVI & LAI


```{r ndvi_pre}

inputPanel(
  selectInput("index", label = "Index:",
              choices = c("NDVI", "LAI"), selected = "NDVI"),
  
  selectInput("year", label = "Year:",
              choices = c(2017,2018), selected = 2017),
  
  sliderInput("month", label = "Month:",
              min = 4, max = 8, value = 1, step = 1)
)

renderPlot({
  if(input$year==2017){
    a <- c("20170406","20170501","20170602","20170609","20170828")
    date <- a[input$month-3]
  }else{
    a <- c("20180409","20180504","20180520","20180628","20180909")
    date <- a[input$month-3]
  }
  
  filename <- paste(input$index,date,".Tif",sep='')
  library(raster)

  index_plot <- raster(filename)
  plot(index_plot)
  
})
```



## Extract Data from Sample Points

```{r ndvi_sample}
inputPanel(
  selectInput("index2", label = "Index:",
              choices = c("NDVI", "LAI"), selected = "NDVI"),
  
  selectInput("year2", label = "Year:",
              choices = c(2017,2018), selected = 2017)
)


renderPlot({
library(ggplot2)  
setwd("D:/R/demmin")
filename <- paste("Data_ww",input$year2,".csv",sep="")
Data_ww <- read.csv(filename)
eval(parse(text=paste('ggplot(Data_ww,aes(x=date+3, y=',input$index2,', color=Pt))+geom_point()+stat_smooth()+ggtitle("',paste(input$index2,input$year2,sep=""),'")')))

})
```

## Temperature
```{r temp}
inputPanel(
  selectInput("year3", label = "Year:",
              choices = c(2017,2018), selected = 2017)
)


renderPlot({
library(ggplot2)  

filename <- paste("Data_Temp",input$year3,".csv",sep="")
Data_temp<- read.csv(filename)

ggplot(Data_temp,aes(x=date, y=Temp, col=month))+geom_point()+facet_wrap(~month)+stat_smooth()

})
```


## Conclusion

- steeper rise and decline in NDVI/LAI 2018   => shortened green period

- early warm season and consistant hot days in 2018 => drough

- heat wave in 2018 => worse vegetation growth


